Conflict Analysis for Mixed-integer SDPs

### 2022-08-01 tex/ConflictAnalysis.tex
add case with all fixed variables
add something on the infeasible case
some fixes

Note that in~\eqref{eq:dual} there is only one affine constraint, which
implies that there exists a rank-1 solution. Thus, we are aiming to
construct a rank-1 solution $X^* = x^* (x^*)\T \succeq 0$.  This solution
has to satisfy:
\[
0 = \skal{\mu^* A - B}{x^* (x^*)\T} = (x^*)\T (\mu^* A - B) x^*.
\]
Therefore, $x^*$ needs to be an eigenvector for the eigenvalue~$0$ of
$\mu^* A - B$ and thus $x^* \in \ker(\mu^* A - B)$. Moreover,
$\skal{A}{x^*(x^*)\T} = (x^*)\T A x^* = \gamma$ needs to hold.  Consider a
generator matrix $C \in \R^{n \times r}$ of the kernel of $\mu^* A - B$,
i.e., $\ker(\mu^* A - B) = \{C y \suchthat y \in \R^r\}$.  Then by scaling,
the problem reduces to the question whether there exists $y \in \R^r$ such
that
\[
y\T C\T A C y
\begin{cases}
  > 0 & \text{if } \gamma > 0,\\
  < 0 & \text{if } \gamma < 0.
\end{cases}
\]
Computing a maximal/minimal eigenvalue/eigenvector of $C\T A C$ will decide
this.

@@

>>>>

Note that in~\eqref{eq:dual} there is only one affine constraint, which
implies that there exists a rank-1 solution. Thus, we are aiming to
construct a rank-1 solution $X^* = x^* (x^*)\T \succeq 0$.  This solution
has to satisfy:
\[
0 = \skal{\mu^* A - B}{x^* (x^*)\T} = (x^*)\T (\mu^* A - B) x^*.
\]
Since $\mu^* A - B \succeq 0$, there exists a matrix
$D \in \R^{k \times n}$ such that $D\T D = \mu^* A - B$. Thus, we are
searching for $x^*$ with $(D x^*)\T D x^* = 0$. Therefore,
$x^* \in \ker(D)$. In fact,
$\ker(D) = \ker(\mu^* A - B)$.\footnote{Clearly,
  $\ker(D) \subseteq \ker(\mu^* A - B)$. Conversely, let
  $x \in \ker(\mu^* A - B)$. Then
  $(Dx)\T Dx = \norm{Dx}_2^2 = (\mu^* A - B)x = 0$. But then $Dx = 0$.}
Moreover, $\skal{A}{x^*(x^*)\T} = (x^*)\T A x^* = \gamma$ needs to hold.
Consider a generator matrix $C \in \R^{n \times r}$ of the kernel of
$\mu^* A - B$, i.e., $\ker(\mu^* A - B) = \{C y \suchthat y \in \R^r\}$.
Then by scaling, the problem reduces to the question whether there exists
$y^* \in \R^r$ such that
\[
(y^*)\T C\T A C y^*
\begin{cases}
  > 0 & \text{if } \gamma > 0,\\
  < 0 & \text{if } \gamma < 0.
\end{cases}
\]
Computing a maximal/minimal eigenvalue/eigenvector of $C\T A C$ will decide
this.

@@

\paragraph{Case 4, infeasible:}

If~\eqref{eq:basic} is infeasible, we are searching for a rank-1 solution
$X^* = (x^*)\T x^*$ such that
\[
\skal{B}{X^*}
\begin{cases}
 > 0 & \text{if } \gamma > 0,\\
 < 0 & \text{if } \gamma < 0
\end{cases}
\]
and $\skal{A}{X^*} = 0$ (and $\alpha^* = \beta^* = 0$). Let again $C^{n
  \times r}$ be a generator matrix of $\ker(A)$ and compute
\[
y\T C\T B C y
\begin{cases}
  > 0 & \text{if } \gamma > 0,\\
  < 0 & \text{if } \gamma < 0.
\end{cases}
\]
By scaling, this produces the wanted solution.

% -------------------------------------------------------------------------
\subsubsection{SDPs with All Fixed Variables}

Consider the general problem with fixed variables:
\[
  \inf\; \{ b\T y \suchthat \sum_{i=1}^m A^i\, y_i - A^0 \succeq 0,\; \ell \leq y \leq \ell\},
\]
and its dual:
\[
  \sup\; \{\skal{A^0}{X} + \ell\T \alpha - \ell\T \beta \suchthat \skal{A}{X} +
  \alpha_i - \beta_i = b_i\; \forall i \in [m],\; X \succeq 0,\; \alpha,\; \beta \geq 0\}.
\]
We can take
\[
X^* = 0,\quad
\alpha^*_i = \max\,\{0, b_i\}, \quad
\beta^*_i = -\min\,\{0, b_i\}.
\]
This solution is feasible for the dual and has objective value $\ell\T b$.
